The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-11 Writeup/paper_v3.tex
Conversation about linecolors and marker sizes removed

\claire{Maybe don't use red and green. It's not an uncommon color-blindness.} \arun{Use black instead of green maybe? Cyan and Magenta aren't very contrasting from blue and red resp.}\claire{black would be fine, or green with larger symbols, since those also differentiate the densities.} 
For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).

>>>>

%\claire{Maybe don't use red and green. It's not an uncommon color-blindness.} \arun{Use black instead of green maybe? Cyan and Magenta aren't very contrasting from blue and red resp.}\claire{black would be fine, or green with larger symbols, since those also differentiate the densities.} 
For figures up to Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).
